### 2017-04-13 paper/oopsla17-submission/learning.tex
more kamalika notes

\subsection{Labels}
\label{sec:labels}
We define the output of the model to be a boolean label, where ``false''
means the expression \emph{should not} change and ``true'' means the
expression \emph{should} change.
%
This allows us to predict whether any individual expression should
change, but we would actually like to predict the \emph{most likely}
expressions to change.
%
Many learning algorithms produce not only a prediction, but also a
metric that can be interpreted as a \emph{confidence} in the prediction.
%
Thus, we \emph{rank} the expressions by the model's confidence that they
will change, and select only the top $k$ (in practice $k=3$) to present
to the user.

>>>>

\subsection{Labels}
\label{sec:labels}
Recall that we make predictions in two stages.
%
First, we use $\evalsym$ to predict for each subexpression whether it
should be blamed, and extract a confidence score $\mathcal{P}$ from the
$\Model$.
%
Thus, we define the output of the $\Model$ to be a boolean label, where
``false'' means the expression \emph{should not} change and ``true''
means the expression \emph{should} change.
%
This allows us to predict whether any individual expression should
change, but we would actually like to predict the \emph{most likely}
expressions to change.
%
Second, we \emph{rank} each subexpression by the confidence $\mathcal{P}$
that it should be blamed, and return to the user the top $k$
most likely blame assignments (in practice $k=3$).

% Many learning algorithms produce not only a prediction, but also a
% metric that can be interpreted as a \emph{confidence} in the prediction.
% %
% Thus, we \emph{rank} the expressions by the model's confidence that they
% will change, and select only the top $k$ (in practice $k=3$) to present
% to the user.
